Predicting Political Support in the United States

### 2024-03-15 output/paper.qmd
Change figs to tables

```{r}
#| label: fig-modelsummarycultural
#| fig-cap: "Explaining whether a voter supported Biden or Trump in 2020 given their gender, age, race, and religion"
#| message: false
#| warning: false
#| echo: false

@@

```{r}
#| label: fig-modelsummaryimportances
#| fig-cap: "Explaining whether a voter supported Biden or Trump in 2020 given their education, household gun ownership, and student load status."
#| message: false
#| warning: false
#| echo: false

>>>>

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: tbl-modelsummarycultural
#| tbl-cap: "Explaining whether a voter supported Biden or Trump in 2020 given their gender, age, race, and religion"

@@

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: tbl-modelsummaryimportances
#| tbl-cap: "Explaining whether a voter supported Biden or Trump in 2020 given their education, household gun ownership, and student load status."
